\begin{declaration}

\vspace{1cm}

I, \authorname, declare that this thesis and the work presented in it are my own, done while in candidature for a doctorate degree.
This thesis was not used, in whole or in part, to achieve an academic degree.
No external sources were used without declaration in the text: any thoughts from others or literal quotations are clearly marked and where I have quoted from the work of others, the source is always given.
Except for such quotations, this thesis is entirely my own work.\\

Several studies and results presented in this document have already been published, either in proceedings of the \acrfull{IPAC} or as a peer-reviewed article in \acrfull{PRAB}, and a summary of these references is given below.\\

The following articles report on work that was included in this thesis:
\newline \newline
\noindent\cite{IPAC:Soubelet:Prospect_IR_Coupling_Correction_LHC_Run3}: F. Soubelet \textit{et al.}, "Prospects for Local Interaction Region Coupling Correction at the LHC in Run~\num{3}", in Proceedings of \num{12}th Int. Particle Accelerator Conf. (IPAC'21), Campinas, Brazil, MOPAB007, \num{2021}.
\newline \newline
\noindent\cite{IPAC:Soubelet:First_Corrections_IR_Local_Coupling_LHC_Run3}: F. Soubelet \textit{et al.}, "First Interaction Region Local Coupling Corrections in the LHC Run~\num{3}", in Proceedings of \num{13}th Int. Particle Accelerator Conf. (IPAC'22), Bangkok, Thailand, WEPOPT007, \num{2022}.
\newline \newline
\noindent\cite{IPAC:Soubelet:Supervised_Machine_Learning_Local_Coupling_Sources_Detection_LHC}: F. Soubelet \textit{et al.}, "Supervised Machine Learning for Local Coupling Sources Detection in the LHC", in Proceedings of \num{13}th Int. Particle Accelerator Conf. (IPAC'22), Bangkok, Thailand, WEPOPT008, \num{2022}.
\newline \newline
\noindent\cite{PRAB:Soubelet:Rigid_Waist_Shift_Method_Local_Coupling_Correction_LHC_IR}: F. Soubelet \textit{et al.}, "Rigid Waist Shift: A New Method for Local Coupling Corrections in the LHC Interaction Regions", Phys. Rev. ST Accel. Beams \num{26}, \num{2023}.
\newline \newline
\noindent\cite{IPAC:Soubelet:Prospect_Operating_Limited_Skew_Quadrupole_Corrector_Availability_LHC_IR}: F. Soubelet \textit{et al.}, "Prospect of Operating with Limited Skew Quadrupole Corrector Availability in the LHC Interaction Regions", in Proceedings of \num{14}th Int. Particle Accelerator Conf. (IPAC'23), Venice, Italy, MOPL044, \num{2023}.
\newline
\newline
\indent
The following articles are studies that were contributed to by myself but are not included in this thesis:
\newline \newline
\noindent\cite{IPAC:Tomas:Run2_Experience_View_LHC_HLLHC}: F. Carlier \textit{et al.}, "LHC Run~\num{2} Optics Commissioning Experience in View of HL-LHC", in Proceedings of \num{10}th Int. Particle Accelerator Conf. (IPAC'19), Melbourne, Australia, MOPMP033, \num{2019}.
\newline \newline \newline
\noindent\cite{HPC:Tracey:AI_Holistic}: R. Tracey \textit{et al.}, "AI-Driven Holistic Approach to Energy Efficient HPC", in ISC High Performance \num{2020}: High Performance Computing, pp \num{267}-\num{279}, \num{2020}.
\newline \newline
\noindent\cite{REPORT:Apollinari:HL_LHC_TDR}: I. Béjar Alonso \textit{et al.}, "High-Luminosity Large Hadron Collider (HL-LHC): Technical Design Report", in CERN Yellow Reports: Monographs, \num{2020}.
\newline \newline
\noindent\cite{IPAC:Persson:Optics_Correction_Strategy_2021}: T. Persson \textit{et al.}, "Optics Correction Strategy for Run~\num{3} of the LHC", in Proceedings of \num{12}th Int. Particle Accelerator Conf. (IPAC'21), Campinas, Brazil, WEPAB027, \num{2021}.
\newline \newline
\noindent\cite{IPAC:Maclean:Optics_Measurement_Excitation_Betatron_Oscillations_PSB}: E. Maclean \textit{et al.}, "Optics Measurement by Excitation of Betatron Oscillations in the CERN PSB", in Proceedings of \num{12}th Int. Particle Accelerator Conf. (IPAC'21), Campinas, Brazil, THPAB168, \num{2021}.
\newline \newline
\noindent\cite{IPAC:Persson:Optics_Measurements_Correction_Plans_HLLHC}: T. Persson \textit{et al.}, "Optics Measurements and Correction Plans for the HL-LHC", in Proceedings of \num{12}th Int. Particle Accelerator Conf. (IPAC'21), Campinas, Brazil, WEPAB026, \num{2021}.
\newline \newline
\noindent\cite{REPORT:OMC:Optics_Strategy_HLLHC}: X. Buffat \textit{et al.}, "Optics Measurement and Correction Strategies for HL-LHC", in CERN ATS Notes, \num{2022}. %\ TODO: check if this is correct for final version
\newline \newline
\noindent\cite{IPAC:Persson:Optics_Correction_Strategy_2022}: T. Persson \textit{et al.}, "Optics Correction Strategy for Run~\num{3} of the LHC", in Proceedings of \num{13}th Int. Particle Accelerator Conf. (IPAC'22), Bangkok, Thailand, WEPOST008, \num{2022}.
\newline \newline
\noindent\cite{IPAC:Fol:ML_Application_LHC_Optics_Commissioning}: E. Fol \textit{et al.}, "Experimental Demonstration of Machine Learning Application in LHC Optics Commissioning", in Proceedings of \num{13}th Int. Particle Accelerator Conf. (IPAC'22), Bangkok, Thailand, MOPOPT047, \num{2022}.
\newline \newline
\noindent\cite{IPAC:Carlier:Challenges_kmodulation_LHC_Run3}: F. Carlier \textit{et al.}, "Challenges of k-Modulation Measurements in the LHC Run~3", in Proceedings of \num{14}th Int. Particle Accelerator Conf. (IPAC'23), Venice, Italy,  MOPL014, \num{2023}.
\newline \newline
\noindent\cite{IPAC:Carlier:LHC_Run3_Optics_Correction}: F. Carlier \textit{et al.}, "LHC Run~3 Optics Correction", in Proceedings of \num{14}th Int. Particle Accelerator Conf. (IPAC'23), Venice, Italy,  MOPL015, \num{2023}.
\newline \newline
\noindent \cite{PRAB:Dilly:First_Operational_Dodecapole_Correction_LHC}: J. Dilly \textit{et al.}, "First Operational Dodecapole Correction in the LHC", Phys. Rev. ST Accel. Beams \num{26}, \num{2023}.
\newline \newline

\end{declaration}

\cleardoublepage